---
title: "C9W4Slidify"
author: "SatyaBharat"
date: "October 20, 2017"
output: ioslides_presentation
---

## Introduction to problem statement

The data set is a collection of work that is being performed to clients where the complexity of the applications are derived based on the application source code.This data set has the below colums

- Vertical (which industry segment the client is from)
- Country (which country the client has head quarters)
- Maskname (dummy name to client)
- FY (finalcial Year)
- Quarter (in which quarter the analysis is performed)
- Total LOC (Overall lines of code)
- Effective LOC (Executable line of code excluding blank lines and comments)
- Halstead , McCabe, McClure (complexity metrics)
- Technical (derived technical complexty)
- dead, redundant (% of code in applications)

## Data set Information

```{r cars, echo = TRUE, warning=FALSE, message=FALSE}
inputd <- read.csv("prjInput.csv", header=TRUE)
colnames(inputd)[1]<- "vertical"
colnames(inputd)[6]<-"loc"
colnames(inputd)[7]<-"effloc"

names(inputd)
head(inputd)
```
## Functionality

This application provides users options to select the industry segment and country.
With the two inputs from the overall data set the subset dataset is derived.

Aggregated with loc~FY+Quarter 
Plotter with the resulted information.

```{r}
     fltr1 <- subset(inputd, (inputd$vertical == "Insurance" & inputd$Country == "USA"))
     
     fltr1$loc = as.numeric(fltr1$loc)
     
     fyloc <- aggregate(loc~FY+Quarter, data=fltr1, FUN=sum)
```

## Slide with Plot

```{r }
plot(fyloc,fltr1$vertical)
```

